---
title: "Untitled"
author: "Jonathan Bourne"
date: "20/05/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---




#some core periphery stuff
Core-periphery structure requires something else in the network 
https://arxiv.org/pdf/1710.07076.pdf

This one could be implemented in R
A Fast Algorithm for the DiscreteCore/Periphery Bipartitioning Problem
https://arxiv.org/pdf/1102.5511.pdf

```{r}

packages <- c("tidyverse", "igraph","readr","readxl", "broom", "stringr", "xtable", "rlang", "latex2exp", "yardstick", "minpack.lm", "ggraph", "patchwork", "rsample", "VGAM", "class", "mclust", "R.matlab", "ranger")

new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

select <- dplyr::select
arrange <- dplyr::arrange
map <- purrr::map
sapply(packages, library, character.only = TRUE)

library(NetworkSpringEmbedding)

#Set up file system to read the correct folders this switches between aws and windows mode

#basewd <- "/home/jonno/Dropbox/Jonathan_Bourne_Phd_Folder"
LatexFolder <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Sets Paper 1" 
FiguresFolder <- file.path(LatexFolder, "Figures")
TablesFolder <- file.path(LatexFolder, "Tables")
MatricesFolder <- file.path(LatexFolder, "Matrices")
PLwd <- "/home/jonno/setse_1_data"
CodeFolder <- "/home/jonno/SETSe_assortativity_and_clusters"
SubcodeFolder <- file.path(CodeFolder, "sub_code")

#Load some other useful functions
list.files("/home/jonno/Useful_PhD__R_Functions", pattern = ".R", full.names = T) %>%
  walk(~source(.x))


ReedFolder <- file.path(PLwd, "Reed_Nelson")

```


#Reed Nelson

This chunk does and exploration of the data that Reed Nelson gave me

The profit making metera has notably higher edge density


```{r}
brazil_files <-list.files(file.path(ReedFolder, "north_american_brazil"), full.names = T)


lamp_g <- graph_from_data_frame(read_csv(brazil_files[2]), directed = F, vertices = read_csv(brazil_files[1])) %>%
  remove_small_components()

lamp_list <- lamp_g %>% as_data_frame(., what = "both")

lamp_edge <-lamp_list$edges %>%
  mutate(weight = case_when(
    weight =="A"~15,
    weight =="B"~25,
    weight == "C"~35,
    TRUE ~as.numeric(weight)
  ))

lamp_g <- graph_from_data_frame(lamp_edge, directed = FALSE, vertices = lamp_list$vertices)


test <- as_data_frame(lamp_g)

ecount(lamp_g)/vcount(lamp_g)

plot(lamp_g)

lapdog_g <- graph_from_data_frame(read_csv(brazil_files[4]), directed = T, vertices = read_csv(brazil_files[3])) %>%
  remove_small_components()

lapdog_list <- lapdog_g %>% as_data_frame(., what = "both")

lapdog_edge <-lapdog_list$edges %>%
  mutate(weight = case_when(
    weight =="A"~15,
    weight =="B"~25,
    weight == "C"~35,
    TRUE ~as.numeric(weight)
  ))

lapdog_g <- graph_from_data_frame(lapdog_edge, directed = FALSE, vertices = lapdog_list$vertices)

ecount(lapdog_g)/vcount(lapdog_g)

plot(lapdog_g)

metera_g <- graph_from_data_frame(read_csv(brazil_files[6]), directed = T, vertices = read_csv(brazil_files[5])) %>%
  remove_small_components()

plot(metera_g)

ecount(metera_g)/vcount(metera_g)

lamp_g %>%
  ggraph() +
    geom_edge_link() +
  geom_node_point(aes( colour = class), size = 7) +
geom_node_text(aes(label = name))+
  ggtitle("lamp")
  NULL


lamp_embeddings <- lamp_g %>%
  prepare_SETSe_binary(., node_names = "name", k = 1000, force_var = "class", positive_value = "Finance & HR") %>%
  auto_SETSe() %>%
  map(~{.x %>% mutate(graph_id = "lamp")})

lapdog_embeddings <- lapdog_g %>%
  prepare_SETSe_binary(., node_names = "name", k = 1000, force_var = "class", positive_value = "Finance & HR") %>%
  auto_SETSe() %>%
  map(~{.x %>% mutate(graph_id = "lapdog")})

g <- metera_g  %>%
  set_edge_attr(., "k", value = edge_attr(., "weight")*100)

test <- c("lamp_g", "lapdog_g", "metera_g") %>%
  map(~{
    
  graph_name <- .x
  temp <- get(.x)  %>%
    set_vertex_attr(., "node_name", value = vertex_attr(., "name")) %>%
  set_edge_attr(., "k", value = edge_attr(., "weight")*100) %>%
  categorical_SETSe(., "node_name", node_names = "name", k = "k") %>%
    map(~{ .x %>% 
        mutate(graph_id = graph_name)
      })

  }) %>%
  transpose() %>%
  map(~{bind_rows(.x)})
  


test$node_details %>%
  ggplot(aes(x = mean_strain, y = mean_elevation, colour = class)) +
  geom_point()+
  facet_wrap(~graph_id)

test$node_details %>%
group_by(graph_id) %>%
  summarise_if(is.numeric, ~median((.)))

test2 <- test$node_details %>%
  select(-class_2,-node) %>%
  group_by(graph_id, class) %>%
  summarise_all(list(mean))

#although lamp and metera have similar tension, lapdog has easily the highest tension of the three networks
#The overall mean absolute elevation of metera is much lower than the other two. This is becuase 

node_details_df <- test$edge_embeddings %>%
  separate(., col = edge_name, into = c("from", "to")) %>%
  pivot_longer(cols = from:to, , values_to = "node") %>%
  select(-name) %>%
  group_by(node) %>%
  summarise_all(mean) %>%
  left_join(., test$node_embeddings) %>%
  left_join(as_data_frame(g, what = "vertices"), by = c("node" ="name")) %>%
  arrange(as.numeric(node))

test2 %>%
ggplot(aes(x = (euc_strain), y = euc_elevation, color = class)) + geom_point()


tsne_out <-Rtsne(test$dist_node %>% select(-node), perplexity = 5)

bind_cols(test2,
tibble(tsne_x = tsne_out$Y[,1],
       tsne_y = tsne_out$Y[,2])
) %>%
  ggplot(aes(x = tsne_x, y = tsne_y, color = class)) +  geom_point()

```

##accounting firms

This is data from the accounting firms Reed sent me
```{r}
accounting_files <-list.files(file.path(PLwd, "/Reed_Nelson/accounting_firms"), full.names = T)

create_accountancy <- function(n, symmetric = FALSE){
  
  directed <- TRUE
  
  temp <- read_csv(accounting_files[n+1], col_names = F) %>% 
    mutate(from = paste0("X",1:nrow(.)))%>%
    pivot_longer(cols = -from, names_to = "to", values_to = "value") %>%
    filter(value !=0) 
  
  #makes the data frame symmetric, where the matrix is transposed and added
  if(symmetric){
    
    directed <- FALSE
    
    temp2 <- temp %>%
      rename(from = to, to = from)
    
    temp <- bind_rows(temp, temp2) %>%
      group_by(from, to)  %>%
      summarise(weight = sum(value))
    
  }
  
  g <- temp %>%
    graph_from_data_frame(., directed = directed, 
                          vertices = read_csv(accounting_files[n], col_names = T) %>%
                            separate(., col = data, into = c("comp_id", "person_name"), sep = "-")  %>% 
                            mutate(name = paste0("X",1:nrow(.)), node_id = paste0("X",1:nrow(.))) %>%
                            select(name, everything())
    )

  if(symmetric){
    
    g <- g %>%
      simplify()
    
  }
  
  return(g)
}

Rota <- create_accountancy(1, symmetric = T)
Sabio <- create_accountancy(3, symmetric = T)
SAT1 <- create_accountancy(5, symmetric = T)
SAT2 <- create_accountancy(7, symmetric = T)


test <- c("Rota", "Sabio", "SAT1", "SAT2") %>%
  map(~{
    
  graph_name <- .x
  g <- get(.x) 
  temp <- g  %>%
  set_edge_attr(., "k", value = edge_attr(., "weight")*100) %>%
  categorical_SETSe(., force_var = "person_name", node_names = "name", k = "k") %>%
    map(~{ .x %>% 
        mutate(graph_id = graph_name)
      })

  }) %>%
  transpose() %>%
  map(~{bind_rows(.x)})




test2 <- test$node_details

test2 %>%
  ggplot(aes(x = mean_tension, y = mean_elevation, colour = core_node)) + geom_point() +
  facet_wrap(~graph_id) +
  labs(title = "tension and strain of 1 vs all analysis of 4 accounting firms")

```

#four hospitals

```{r}

hospital_files <- list.files(file.path(ReedFolder, "hospitals", "raw_data"), full.names = T)

file_name <-hospital_files[5]

extract_graph_from_AT_output <-function(file_name, symmetric = TRUE){
  
  directed = TRUE
  
  org_lines <- read_lines(file_name)
  
  #find the first row of the matrix
  mat_start <- grep(org_lines, pattern = "Blocked Adjacency Matrix")+6
  #find the last row of the matrix
  mat_end <- grep(org_lines, pattern = "Density matrix")-5
  #get the position the limits of the matrix and the core periphary divider
  mat_col_limits <- gregexpr(pattern = "\\|", text = org_lines[mat_start])[[1]]
  
  #get the point at which the core periphery split is found. diveded by two as there is a space between each columns
  core_periph_limit <- (mat_col_limits[2]-mat_col_limits[1])/2
  
  clean_row <- org_lines[mat_start:mat_end][-core_periph_limit] %>%
    map_chr(~{
      print(.x)
      str_sub(.x, start =mat_col_limits[1]+1, end =  mat_col_limits[3]-2) %>%
        str_remove(., " \\|")
      
    })
  
  edge_list <- 1:length(clean_row) %>%
    map_df(~{
      occs <- gregexpr(pattern = "[0-9]", text = clean_row[.x])[[1]]
        tibble(from = .x, to = as.integer(occs/2),
               value = 1)
    }) %>%
    filter(to!=0) #if there is nothing on the row an index of -1 is returned, this is converted to 0... thus all zeros are removed
  
    if(symmetric){
    
    directed <- FALSE
    
    edge_list2 <- edge_list %>%
      rename(from = to, to = from)
    
    edge_list <- bind_rows(edge_list, edge_list2) %>%
      group_by(from, to)  %>%
      summarise(weight = sum(value))
    
  }
  
  nodes <-  org_lines[mat_start:mat_end][-core_periph_limit] %>%
    map_df(~{

    info_string  <- str_sub(.x, start =1, end = mat_col_limits[1]-1)
       #match any letter followed by at least one of anything that is not whitespace.. this allows accents
   name_id <- str_extract(info_string, "[aA-zZ][^ ]+")
   node_id <- str_extract(info_string, "[0-9]+")
   
   tibble(name_id = name_id, node_id = node_id)

    }) %>%
    mutate(node = 1:n(), core_node = node<core_periph_limit) %>%
    select(node, everything())
  
  
  g <- graph_from_data_frame(edge_list, directed = directed, vertices = nodes)
  
    if(symmetric){
    
    g <- g %>%
      simplify()
    
  }
  
  return(list(edge_list = edge_list, nodes = nodes, g= g))
  
}


#save the csv files
hospital_files %>%
  walk(~{
    
    file_name <- basename(.x) %>% str_remove(., "cent per ") %>% str_remove(., ".txt")
    
    graph_data <- extract_graph_from_AT_output(.x)
    
    write_csv(graph_data$edge_list, path = file.path(ReedFolder, "hospitals",  paste0(file_name, ".csv") ))
    
    write_csv(graph_data$nodes, path = file.path(ReedFolder, "hospitals",  paste0(file_name, "_nodes.csv") ))
  
      
  })


#missing 27 and 18 I assume 18 is also a nurse
santa_helena_roles <- c(c("Psychologist", "Supervisor Maintenance", "Supervisor Cleaning", "Supervisor Cleaning", rep("Nursing", 11),
  "Manager Human Resources"),
c("Supervisor Housekeeping", "Nutritionist", "Nutritionist", "Administrator", "Manager Pharmacy", "Manager Pharmacy", "Social Worker",
  "Wocial Worker", "Billing", "Billing"))


santa_rosa_roles <- c(c("Superintendent", "Coordinator HR", "Coordinator Nursing", "Cooordinator Patient Relations",  "Coordinator Supplies",  "Coordinator Financial",  "Coordinator IT", "Coordinator Pharmacy",  "Auditing", "Quality Control", rep("Nursing", 7), "Coordinator ICU",
  "Coordinator Housekeeping", "Coordinator Admissions"),
c("Coordinator Surgery Center", "Coordinator Security", "Manager Planning", "Financial Director", "Administrator"))

femina <-extract_graph_from_AT_output(hospital_files[1])$g
hgu <-extract_graph_from_AT_output(hospital_files[2])$g
hmvg <-extract_graph_from_AT_output(hospital_files[3])$g

#the first string vector is the core the second is the periphery, there is no reason for them being separate except that I got the data in that format.
santa_helena <- extract_graph_from_AT_output(hospital_files[4])$g %>% set_vertex_attr(., "role", value = santa_helena_roles)

santa_rosa <-extract_graph_from_AT_output(hospital_files[5])$g %>% set_vertex_attr(., "role", value = santa_rosa_roles)

hospital_embeddings <- c("femina", "hgu", "hmvg", "santa_helena", "santa_rosa") %>%
  map(~{
    
  graph_name <- .x
  g <- get(.x) %>%
    set_vertex_attr(., "node_names", value = 1:vcount(.))
  temp <- g  %>%
  set_edge_attr(., "k", value = edge_attr(., "weight")*100) %>%
  categorical_SETSe(., force_var = "name", node_names = "node_names", k = "k") %>%
    map(~{ .x %>% 
        mutate(graph_id = graph_name)
      })

  }) %>%
  transpose() %>%
  map(~{bind_rows(.x)})



hospital_embeddings$node_details %>%
  ggplot(aes(x = mean_tension, y = mean_elevation, colour = core_node)) + geom_point() +
  facet_wrap(~graph_id) +
  labs(title = "comparison of core periphery with SETSe placement")

hospital_embeddings$node_details %>%
  filter(!is.na(role)) %>%
  mutate(is_nurse = ifelse(grepl(role, pattern = "Nurs"), "Nursing", "Other")) %>%
    ggplot(aes(x = mean_tension, y = mean_elevation, colour = is_nurse)) + geom_point() +
  facet_wrap(~graph_id)+
  labs(title = "Comparison of nursing teams within a hospital using SETSe")

```


#bni
business network international 
```{r}


load_bni <- function(file_path, directed = FALSE){
  
  load_data <-read_csv2(file_path) %>%
    slice(-67) %>%
    select(-Rows)%>%
    separate(col = "X1", into = c("node", "name_id"), sep = "-") %>%
  separate(col = name_id, into = c("rep", "company"), sep = " ", extra = "merge")
  
  nodes <- load_data %>% select(node, rep, company)
  
  edge_list <- load_data %>% select(-rep, - company) %>%
    pivot_longer(cols= -node, names_to = "to", values_to = "value") %>%
    filter(value!=0) %>%
    rename(from = node)
  
  if(!directed){
    
    edge_list2 <- edge_list %>%
      rename(from = to, to = from)
    
    edge_list <- bind_rows(edge_list, edge_list2) %>%
      group_by(from, to)  %>%
      summarise(weight = sum(value))
    
  }
  
  g <- graph_from_data_frame(edge_list, directed = directed, vertices = nodes)
  
  if(!directed){
    
    g <- g %>%
      simplify()
    
  }
  
  return(g)
}

file_path <- file.path(ReedFolder, "bni", "bnifriendexcel.csv")

bni_files <- list.files(file.path(ReedFolder, "bni"), full.names = T)

bni_frequency_g <-load_bni(bni_files[1]) %>%
    set_vertex_attr(., "node_names", value = 1:vcount(.))

bni_friends_g <-load_bni(bni_files[2]) %>%
    set_vertex_attr(., "node_names", value = 1:vcount(.))

bni_references_g <-load_bni(bni_files[3]) %>%
    set_vertex_attr(., "node_names", value = 1:vcount(.))

bni_trust_g <-load_bni(bni_files[4]) %>%
    set_vertex_attr(., "node_names", value = 1:vcount(.))

#avra has no visits
bni_visits_g <-load_bni(bni_files[5]) %>%
    set_vertex_attr(., "node_names", value = 1:vcount(.))


bni_setse_list <- ls(pattern = "bni_.+_g") %>%
  map(~{
    
    type_name <- .x %>% str_remove(., "bni_") %>% str_remove(., "_g")
    
    print(type_name)
    out <-get(.x) %>%
      set_vertex_attr(., "centrality", value = centr_betw(., directed = F)$res) %>%
      set_vertex_attr(., "degree", value = degree(.)) %>%
      set_edge_attr(., "k", value = edge_attr(., "weight")*100) %>%
      remove_small_components() %>%
      categorical_SETSe(., force_var = "name", node_names = "node_names", k = "k") %>%
      map(~{.x %>% mutate(type = type_name)})
    
    return(out)
    
  }) %>% transpose
  


refferals_recieved <- as_data_frame(bni_references_g) %>%
  #left_join(as_data_frame(bni_references_g, what = "vertices"), by = c("to"="name")) %>%
  group_by(to) %>%
  summarise(refferals_recieved = sum(weight),
   #         company = first(company)
   ) %>%
  rename(node = to)

refferals_given <- as_data_frame(bni_references_g) %>%
  #left_join(as_data_frame(bni_references_g, what = "vertices"), by = c("to"="name")) %>%
  group_by(from) %>%
  summarise(refferals_given = sum(weight),
   #         company = first(company)
   ) %>%
  rename(node = from)

test <- bind_rows(bni_setse_list$node_details ) %>%
  left_join(.,test %>% filter(type == "references") %>%
              select(node, elev2 = mean_elevation)) %>%
  left_join(refferals_recieved)  %>%
  left_join(refferals_given) %>%
  mutate(refferals_given = ifelse(is.na(refferals_given), 0, refferals_given),
         refferals_recieved = ifelse(is.na(refferals_recieved), 0, refferals_recieved),
         tot_ref = refferals_given+refferals_recieved)

test %>%
  ggplot(aes(x = mean_tension, y = mean_elevation , color = company)) + geom_point() +
 # gghighlight(mean_elevation< -0.01, mean_tension>0.15) +
  
  labs(title = "BNI relationships in SETSe space")



test %>%
  ggplot(aes(x = mean_tension, y = mean_elevation)) +
  facet_wrap(~type) +
  geom_point() +
#  gghighlight(rank(mean_tension)<3 & rank(mean_elevation)<3) +
   gghighlight(company %in% c("AVRA", "FEDERAL INVEST", "ZAPPSTI")) +
     geom_point(aes(colour = company)) +
  labs(title = "BNI relationships in SETSe space")



test %>%
  ggplot(aes(x  = mean_elevation)) +
  facet_wrap(~type) +
  geom_density() 
  

test %>%
  group_by(type) %>%
  mutate(rank_type = rank(mean_elevation)) %>%
  ggplot(aes(x = refferals_recieved, y = refferals_given)) +
    facet_wrap(~type) +
  geom_point(aes(colour = rank_type)) +
  scale_color_viridis_c() 


test2 <- test %>%
  select(node, refferals_recieved, refferals_given, type, mean_elevation, company, elev2, tot_ref) %>%
  pivot_wider(names_from = type, values_from = mean_elevation) %>%
  mutate(tot_ref_sqrt = log(tot_ref),
         visits2 = visits^2)

ref_mod <- lm(tot_ref_sqrt~visits, data = test2)

summary(ref_mod)

active_formula <- tot_ref_sqrt~visits

summary( lm(active_formula, data = test2))$r.squared

annotations_df <- names(test2)[7:11] %>%map_df(~{
r_val <- as.formula(paste0("tot_ref_sqrt~", .x)) %>%
    lm(., data = test2) %>%
    summary(.) %>% .$r.squared 

x_pos <- test %>% filter(type ==.x) %>% pull(mean_elevation) %>% mean

tibble(type = .x, r_val = paste0("R^2=",round(r_val, 3)), x = x_pos, y = 1)
})


test %>%
  ggplot(aes(x = mean_elevation, y = log(tot_ref))) +
  geom_point() +
  facet_wrap(~type, scales = "free_x") +
  scale_color_viridis_c() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "relationship between SETSe embeddings and total references",
       x = "mean elevation",
       y = "logarithm of total references recieved and given") +
  geom_text(data = annotations_df, aes(x = x, y = y, label = r_val))


test %>%
  ggplot(aes(x = log(centrality), y = log(tot_ref))) +
  geom_point() +
  facet_wrap(~type, scales = "free_x") +
  scale_color_viridis_c() +
  geom_smooth(method = "lm", se = FALSE)

```

```{r}


```

